Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes

### 2025-05-03 products/manuscript/supplement/Supplementary-Material.qmd
update

---
title: "Supplement Materials of Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
resources:
  - Images/**
execute:
  root: products/manuscript
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

>>>>

---
title: "Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography:
  - ../../../assets/dataanalysis-references.bib
csl: ../../../assets/american-journal-of-epidemiology.csl
---
